---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# feasts
[![Travis build status](https://travis-ci.org/tidyverts/feasts.svg?branch=master)](https://travis-ci.org/tidyverts/feasts)

The R package *feasts* munches on tidy temporal data ([tsibble](https://github.com/tidyverts/tsibble)) to produce time series features, decompositions, statistical summaries and convenient visualisations.

The features offered by *feasts* are essential for the [fable](https://github.com/tidyverts/fable) modelling workflow. It includes convenient functions for exploration prior to modelling, and evaluation after modelling.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tidyverts/feasts")
```

## Example

```{r acf}
library(feasts)
library(tsibbledata)
elecdemand %>% 
  ACF(Temperature, lag.max=48) %>%
  autoplot
```

